### 2009-11-27 doc/tech_doc/client/client_technical.tex
Updating client technical.

\chapter{Grid Flavour Plugins)}
\label{sec:plugins}

@@

\chapter{Job Status mapping}
\label{app:broker-mapping}

The following job states comprises the state model in WS-ARC:
\begin{description}
\item[UNDEFINED] Job state could not be resolved,
\item[ACCEPTED] Job was accepted by the service,
\item[PREPARING] Job is preparing,
\item[SUBMITTING] Job is being submitted to a computing share,
\item[HOLD] Job is put on hold,
\item[QUEUING] Job is on computing share waiting to run,
\item[RUNNING] Job is running on computing share,
\item[FINISHING] Job is finishing,
\item[FINISHED] Job has finished,
\item[KILLED] Job has been killed,
\item[FAILED] Job failed,
\item[DELETED] Job have been deleted,
\item[OTHER] Any job state which does not fit the above states.
\end{description}

\begin{center}
\rowcolors{3}{tablerowcolor}{}
\begin{tabularx}{\textwidth}{CCTCT}
\toprule
\NST{Internal} & \NST{ARC0}  & \NST{ARC1} & \NST{BES} & \NST{CREAM}\\
\midrule
\defineheadfoot
ACCEPTED & ACCEPTED & ACCEPTED & Pending & REGISTERED,\linebreak PENDING\\
PREPARING & PREPARING & PREPARING & \NST{None} & \NST{None} \\
SUBMITTING & SUBMIT & SUBMIT & \NST{None} & \NST{None} \\
HOLD & \NST{None} & \NST{None} & \NST{None} & HELD \\
QUEUING & INLRMS:Q & INLRMS:Q & \NST{None} & IDLE \\
RUNNING & INLRMS:R & INLRMS:R,\linebreak INLRMS:EXECUTED,\linebreak INLRMS:S, INLRMS:E & Running & RUNNING,\linebreak REALLY-RUNNING\\
FINISHING & FINISHING & FINISHING & \NST{None} & \NST{None}\\
FINISHED & FINISHED & FINISHED & Finished & DONE-OK \\
KILLED & KILLED & KILLED & \NST{None} & CANCELLED \\
FAILED & FAILED & FAILED & Failed & DONE-FAILED,\linebreak ABORTED\\
DELETED & DELETED & DELETED & \NST{None} & \NST{None} \\
OTHER & \NST{Any other state} & \NST{Any other state} & \NST{None} & \NST{Any other state} \\
\end{tabularx}
\end{center}

>>>>

\chapter{Grid Flavour Plugins and Commons}
\label{sec:plugins}
With a library utilizing plugins a mapping to a common set of job states
is needed in order to be able to treat jobs from different middlewares
in the same way. In WS-ARC the following job states comprises the state
model which plugins should map their job states:
\begin{description}
\item[UNDEFINED] Job state could not be resolved,
\item[ACCEPTED] Job was accepted by the service,
\item[PREPARING] Job is preparing,
\item[SUBMITTING] Job is being submitted to a computing share,
\item[HOLD] Job is put on hold,
\item[QUEUING] Job is on computing share waiting to run,
\item[RUNNING] Job is running on computing share,
\item[FINISHING] Job is finishing,
\item[FINISHED] Job has finished,
\item[KILLED] Job has been killed,
\item[FAILED] Job failed,
\item[DELETED] Job have been deleted,
\item[OTHER] Any job state which does not fit the above states.
\end{description}
See Appendix~\ref{app:job-status-mapping} for the actual job state
mapping of each of the below described plugins

@@

\chapter{Job Status mapping}
\label{app:job-status-mapping}
\begin{center}
\rowcolors{3}{tablerowcolor}{}
\begin{tabularx}{\textwidth}{CCTCT}
\toprule
\NST{Internal} & \NST{ARC0}  & \NST{ARC1} & \NST{BES} & \NST{CREAM}\\
\midrule
\defineheadfoot
ACCEPTED & ACCEPTED & ACCEPTED & Pending & REGISTERED,\linebreak PENDING\\
PREPARING & PREPARING & PREPARING & \NST{None} & \NST{None} \\
SUBMITTING & SUBMIT & SUBMIT & \NST{None} & \NST{None} \\
HOLD & \NST{None} & \NST{None} & \NST{None} & HELD \\
QUEUING & INLRMS:Q & INLRMS:Q & \NST{None} & IDLE \\
RUNNING & INLRMS:R & INLRMS:R,\linebreak INLRMS:EXECUTED,\linebreak INLRMS:S, INLRMS:E & Running & RUNNING,\linebreak REALLY-RUNNING\\
FINISHING & FINISHING & FINISHING & \NST{None} & \NST{None}\\
FINISHED & FINISHED & FINISHED & Finished & DONE-OK \\
KILLED & KILLED & KILLED & \NST{None} & CANCELLED \\
FAILED & FAILED & FAILED & Failed & DONE-FAILED,\linebreak ABORTED\\
DELETED & DELETED & DELETED & \NST{None} & \NST{None} \\
OTHER & \NST{Any other state} & \NST{Any other state} & \NST{None} & \NST{Any other state} \\
\end{tabularx}
\end{center}
